---
title: "20331568 Data Science Practical Test"
output:
  pdf_document: default
  md_document:
    variant: markdown_github
  html_document:
    df_print: paged
---

## Purpose

The purpose of the project is to create


## Question 1 Solution

## Code used for Figures and Tables

```{r}

```

### Data

I put the unzipped data files in their respective question folders.

For loading in the README - adjust the code.

### Question 1

#### Loading the data

```{r}
q1()


```


#### First plot

It shows that rotten tomatoes movie ratings above 80% 

```{r}
r()
```

The graph below disagrees with above statement. It does the audience score of greater than 85%.

```{r}
rr(e)
```

## LeadsStudio Profitablity 
Disney is seen to be more profitable under Comedy and Anation films. Not ture for all leading studios 

```{r}
dis(b)
```

## World Wide gross rate films

The figure shows that the films with the highest world wide gross above 100 are Comedy. 
I think most people enjoy a good laugh. 

```{r}
h(t)
```



## Question 2

## Data Directory 

```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('D:/20331568/Solution/20331568/Question2/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```

## Data loading:
The data was be cleaned and changed for plotting. 

```{r}
data1()

```


### First plot


It shows that Billonaires under the age of 30. The united states has the highest count. 

```{r}
figure1(g)
```


### Second plot

It shows that the United States has again the richest people with majority of the top 10 Billionaires from there. This is followed by France and India. 

```{r, message=FALSE}
figure2(d)
```



## Question 3 


