---
title: "20331568 Data Science Practical Test"
output:
  pdf_document: default
  md_document:
    variant: markdown_github
  html_document:
    df_print: paged
---

## Purpose

The purpose of the project is to create


## Question 1 Solution

## Code used for Figures and Tables

```{r}
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(pacman)
p_load(tidyverse, lubridate)

# Source in all your functions:
# walk is the 'silent' version of map, which is similar to lapply.
list.files('D:/20331568/Solution/20331568/Question1/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

### Data

I put the unzipped data files in their respective question folders.

For loading in the README - adjust the code.

### Question 1

#### Loading the data

```{r}
#ctrl alt i - load r chunk 

#datcolat <- Data_Collating(Datroot = "Question1/Data/Happy/")


```


#### First plot

I can describe this plot as follows...

It shows that ....

```{r}
# adjust the sizes to fit into the readme a bit.

#g <- Error_bar_plot(datcolat, xaxis_size = 9, xaxis_rows = 3)
#g
```

The second plot in the paper ...

```{r}
 # g <-  Barplot_breakdown_Happy_Contributors(datcolat, Title = "Barplot making up the ladder", Subtitle = "Look at the colours - wow.", xaxis_size = 9, xaxis_rows = 3)
    
#g
```

## Question 2

## Data Directory 

```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('D:/20331568/Solution/20331568/Question2/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```

## Data loading:
```{r}
Loc <- "Question2/data/Wine/"
    dff <- read_rds(glue::glue("{Loc}WineMag.rds"))
    Fruitlist <- read_table("Question2/data/wine/Fruitlist.txt")
    froots <- Fruitlist$Fruits  %>% unique %>% as.list()
    CountryList <- c("South Africa", "Italy", "France", "US", "Spain")

    dff_adj <- dff %>% filter(country %in% CountryList)
```



### First plot

I can describe this plot as follows...

It shows that ....

```{r}

```

### Table of Frequency 

This is a table function with Latex argument so that it can build in html form for use in README.

```{r, message=FALSE}
Tab <- Term_refs_table(dff_adj, Latex = FALSE)
Tab
```


### Second plot

I can describe this plot as follows...

It shows that ....

```{r, message=FALSE}
Tasters <- c( "Lauren Buzzeo" , "Susan Kostrzewa")
df_SA <-
    dff %>% filter(country %in% "South Africa", price > 50, taster_name %in% Tasters)

gg <- Top_5_Wineries_SA_Plot(df_SA, Tasters)
gg
```

### Regression plot

Short overview

```{r, message=FALSE}
Regression_Plot(df_SA)

```

